### 2022-09-20 main/chapter_context.tex
condense a couple of sentences

The \atlas\ detector did not assemble itself into a preordained form.
It results from a large collaborative effort towards a design that would
provide maximally useful and novel data
without exceeding real-world budgets in construction or operation.
Original designs hoped to construct an \atlas\ detector that could
observe the Higgs boson (which was predicted but yet unseen),
precisely measure known massive objects ($W^\pm$, $Z$, $t$),
and possibly discover new particles such as those hypothesized by
supersymmetric models~\cite{atlas1999design1}.
We now review those three goals.

\paragraph{Higgs boson discovery.}
Prior to \atlas' construction, the Higgs boson mass (and existence) was
poorly known, but loosely constrained by results like
$m_H \gtrsim 90\,\eV[G]$ from searches at the
Large Electron–Positron Collider (LEP),
$m_H = 76^{+85}_{-47}\,\eV[G]$ from other data on the electroweak sector,
and $m_H \lesssim 1\,\eV[T]$ from theoretical unitarity arguments~\cite{
atlas1999design2,
ghinculov1998perturb,
lep1999ewk
}.

The Higgs boson couples to an extraordinary variety of fundamental particles,
and \atlas' designers achieved discovery sensitivity across the entire
$100$ to $1000\,\eV[G]$
window by targetting decays including
$H\to b\bar b$,
$H\to \gamma\gamma$,
$H\to ZZ^* \to 4\ell$, and
$H\to ZZ \to \ell\ell\nu\nu$.
This spectrum demands precise measurements of leptons, photons, and
$b$-jets, as well as sensitivity to the missing transverse momentum of
invisible neutrinos for $ZZ \to \ell\ell\nu\nu$ decays at the very highest
masses.

>>>>

The \atlas\ detector did not assemble itself into a preordained form.
It was designed with intent to provide maximally useful and novel data
within real-world cost budgets.
Original designs hoped to construct an \atlas\ detector that could
observe the Higgs boson (which was predicted but yet unseen),
precisely measure known massive objects ($W^\pm$, $Z$, $t$),
and possibly discover new particles such as those hypothesized by
supersymmetric models~\cite{atlas1999design1}.
We now review these three goals with the subsequent news from \atlas'
operations.

\paragraph{Higgs boson discovery.}
Prior to \atlas' construction, the Higgs boson mass (and existence) was
poorly known, but loosely constrained by results like
$m_H \gtrsim 90\,\eV[G]$ from searches at the
Large Electron–Positron Collider (LEP),
$m_H = 76^{+85}_{-47}\,\eV[G]$ from other data on the electroweak sector,
and $m_H \lesssim 1\,\eV[T]$ from theoretical unitarity arguments~\cite{
atlas1999design2,
ghinculov1998perturb,
lep1999ewk
}.
The Higgs boson couples to an extraordinary variety of fundamental particles,
and \atlas' designers achieved discovery sensitivity across the entire
$100$ to $1000\,\eV[G]$
window by targetting decays including
$H\to b\bar b$,
$H\to \gamma\gamma$,
$H\to ZZ^* \to 4\ell$, and
$H\to ZZ \to \ell\ell\nu\nu$.
This spectrum demands precise measurements of leptons, photons, and
$b$-jets, as well as sensitivity to the missing transverse momentum of
invisible neutrinos for $ZZ \to \ell\ell\nu\nu$ decays at the very highest
masses.
